---
title: "Report for the Markov model (cohort state-transition model)"
date: 2020.12.20
header-includes:
   - \usepackage{amsmath}
   - \usepackage{booktabs}
   - \usepackage{fancyhdr}
   - \pagestyle{fancy}
   - \usepackage{array}
   - \usepackage{multirow}
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(xtable)
library(darthtools)
```


# Results from the paper

These two tables are from the result part of the paper by Yaqin Si.
```{r message=FALSE}
strategy_names <- c("strategy1", "strategy2", "strategy3")
# QALY
QALY <- data.frame("est" = c(498,691,654),
                   "LB" = c(103,233,105),
                   "UB" = c(894,194,1108))
rownames(QALY) <- strategy_names
# Prevent CVD events
num_CVD <- data.frame("est" = c(298,374,346),
                   "LB" = c(155,181,154),
                   "UB" = c(441,567,538))
rownames(num_CVD) <- strategy_names
```

```{r, echo=FALSE, results='asis'}
t1 <- kable(QALY, format = "latex", booktabs = TRUE)
t2 <- kable(num_CVD, format = "latex", booktabs = TRUE)
cat(c("\\begin{table}[!htb]
    \\begin{minipage}{.5\\linewidth}
      \\caption{Increased QALY with no screening}
      \\centering",
        t1,
    "\\end{minipage}%
    \\begin{minipage}{.5\\linewidth}
      \\centering
        \\caption{Prevent CVD events}",
        t2,
    "\\end{minipage} 
\\end{table}"
))  
```

\newpage
# Parameters 
```{r}
HR_l_stg1	<- 0.63
HR_m_stg1	<- 1.56
HR_h_stg1	<- 1.6

HR_l_stg2	<- 0.43
HR_m_stg2	<- 0.97
HR_h_stg2	<- 2.06

HR_l_stg3	<- 0.45
HR_m_stg3	<- 1.09
HR_h_stg3	<- 2.11

HR_smk_cvd	<-	0.85
HR_smk_cvdth	<-	0.72
HR_salt_cvd	<-	0.81
HR_salt_cvdth	<-	0.66
HR_wtc_cvd	<-	0.93
HR_wtc_dth	<-	0.93
HR_hpt_lip_cvd	<-	0.7
HR_hpt_lip_cvdth <-	0.82
HR_cvdhistory_cvd <-	1.37
HR_cvdhistory_cvdth <-	3.12

HR_high_live_cvdth <-	1.17
```

# Markov model
## Model input 
```{r, results='asis', message=FALSE}
library(readr)
rate_data <- read_csv("data/ghdx_data.csv")
xtable(data.frame(rate_data),digits=c(0,0,0,6,6,6))
```


```{r}
## General setup
source("./function/transform_func.R")
n_t <- 10   # time horizon, number of cycles
# S1: live; S2: cvd; S3: cvdth; S4: oth_death
v_names_states <- c("S1", "S2", "S3", "S4")  
n_states    <- length(v_names_states)   # number of health states 
v_names_str <- c("Strategy1", "Strategy2", "Strategy3") # store the strategy names
n_str       <- length(v_names_str)      # number of strategies
# Utilities: for calculation of QALY
out_cvd_free <-	1   # utility when being S1
out_cvd <- 0.9   # utility when being S2
out_dth <-	0   # utility when being S3 and S4 together
out_trans_to_cvd <-	-0.038   # TODO


p_live_oth_death <- rate_to_prob(r=rate_data$rate_death_nonCVD,t = n_t)
p_live_cvd <- rate_to_prob(r=rate_data$rate_incidence_CVD,t = n_t)
p_live_cvdth <- rate_to_prob(r=rate_data$rate_death_CVD,t = n_t)


# transition probability from S1 to S2
p_live_cvd_l <- ProbFactor(p_live_cvd,HR_l_stg1)
p_live_cvd_m <- ProbFactor(p_live_cvd,HR_m_stg1)
p_live_cvd_h <- ProbFactor(p_live_cvd,HR_h_stg1)
# transition probability from S1 to S3
p_live_cvdth_l <- ProbFactor(p_live_cvdth,1)
p_live_cvdth_m <- ProbFactor(p_live_cvdth,1.7)
p_live_cvdth_h <- ProbFactor(p_live_cvdth,1)
# transition probability from S2 to S3
p_ccvd_acvd <- ProbFactor(p_live_cvd,HR_cvdhistory_cvd)
p_ccvd_cvdth <- ProbFactor(p_live_cvdth,HR_cvdhistory_cvdth)

```


\begin{center}
\begin{tabular}{cccc } 
\hline
Item & & CVD incidence & CVD cause-specific mortality  \\
\hline
\multirow{3}{6em}{Strategy 1}& {Low risk} & `r HR_l_stg1` & 1   \\
& {Medium risk}& `r HR_m_stg1`  &  1\\
& {High risk}& `r HR_h_stg1`  &  1.7 \\
\hline
\multirow{3}{6em}{Strategy 2}& {Low risk}& `r HR_l_stg2`  & 1 \\
& {Medium risk}  & `r HR_m_stg2` &  1\\
& {High risk}  &`r HR_h_stg2`  &  1.7\\
\hline
\multirow{3}{6em}{Strategy 3}& {Low risk}  & `r HR_l_stg1` & 1 \\
& {Medium risk}  & `r HR_m_stg3` &  1\\
& {High risk}  & `r HR_h_stg3` &  1.7\\
\hline
\multirow{3}{6em}{Intervention}& {Weight control}  & `r HR_wtc_cvd` &  `r HR_wtc_dth`\\
& {Smoke cession}  & `r HR_smk_cvd` & `r HR_smk_cvdth` \\
& {Salt reduction}  & `r HR_salt_cvd` & `r HR_salt_cvdth` \\
\hline
Medication & Statin and antihypertensive &  &  \\
\hline
\end{tabular}
\end{center}

## The component of a Markov model: A transition probability matrix, $P_t$
$$
P_t=
\begin{Bmatrix}
p_{[1,1,t]} & p_{[1,2,t]} & p_{[1,n_s,t]}\\
p_{[2,1,t]} & p_{[2,2,t]} & p_{[2,n_s,t]}\\
...\\
p_{[n_s,1,t]} & p_{[n_s,2,t]} & p_{[n_s,n_s,t]}\\
\end{Bmatrix}
$$

```{r}
###################### Construct state-transition models for Strategy1 #####################
#### Create transition arrays ####
a_P <- array(0, dim      = c(n_states, n_states, n_t),
                dimnames = list(v_names_states, v_names_states, 0:(n_t - 1)))
### Fill in array
## From S1
# a_P["S1", "S1", ]   <- 0
a_P["S1", "S2", ]  <- p_live_cvd_l[1:10]
a_P["S1", "S3", ]   <- p_live_cvdth_l[1:10]
# a_P["S1", "S4", ]   <- 0

## From S2
a_P["S2", "S2", ] <- p_ccvd_acvd[1:10]
a_P["S2", "S3", ] <- p_ccvd_cvdth[1:10]
# a_P["S2", "S4", ]  <- p_ccvd_cvdth[1:10]
```


