---
title: "Report for the Markov model (cohort state-transition model)"
header-includes:
   - \usepackage{amsmath}
   - \usepackage{booktabs}
   - \usepackage{fancyhdr}
   - \pagestyle{fancy}
   - \usepackage{array}
   - \usepackage{multirow}
   # - \usepackage{afterpage}
   - \usepackage{rotating}
output: pdf_document
# classoption: landscape
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(xtable)
library(darthtools)
library(ggplot2)
library(readr)
set.seed(1)
source("function/transform_func.R")
```
# Data and parameters
```{r, results='asis', message=FALSE}
rate_data <- read_csv("data/ghdx_data.csv")
print(xtable(data.frame(rate_data),digits=c(0,0,0,6,6,6),
      caption = "Data from Global Health Data Exchange"),
      caption.placement="top",comment=FALSE)
```


```{r, results='asis', message=FALSE}
population_data <- read_csv("data/Normal3Stra_data.csv")
population_data <- data.frame(population_data)
```

```{r}
n_t <- 10   # time horizon, number of cycles
v_names_states <- c("S1", "S2", "S3", "S4") # S1: live; S2: cvd; S3: cvdth; S4: oth_death 
n_states    <- length(v_names_states)   # number of health states 
v_names_str <- c("Strategy0","Strategy1", "Strategy2", "Strategy3") # store the strategy names
n_str       <- length(v_names_str)      # number of strategies
names_population <- c("m40","m45","m50","m55","m60","m65","m70",
                        "f40","f45","f50","f55","f60","f65","f70")
# Health utilities
out_cvd_free <-	1   # utility when being S1
out_cvd <- 0.9   # utility when being S2
out_dth <-	0   # utility when being S3 and S4 together
out_trans_to_cvd <-	-0.038    

uti_values <- c(out_cvd_free, out_cvd, out_dth, out_dth)
year <- c(1,1,0,0)
HR_cvdhistory_cvd <-	1.37
HR_cvdhistory_cvdth <- 3.12
HR_high_live_cvdth <-	1.17

p_live_oth_death <- rate_to_prob(r=rate_data$death_nonCVD, t = 1)
p_live_cvd <- rate_to_prob(r=rate_data$incidence, t=1)
p_live_cvdth <- rate_to_prob(r=rate_data$death_CVD, t=1)
p_ccvd_acvd <- rate_to_prob(rate_data$incidence*HR_cvdhistory_cvd, t=1)
p_ccvd_cvdth <- rate_to_prob(rate_data$death_CVD*HR_cvdhistory_cvdth, t=1)
# p_acvd_cvddth
```

# A transition probability matrix $P_t$
\begin{center}
\includegraphics[width=8in]{TreeAge.jpg}
\end{center}

\begin{center}
\includegraphics[width=6in]{Mat.png}
\end{center}
$$
P_t=
\begin{Bmatrix}
p_{[1,1,t]} & p_{[1,2,t]} & p_{[1,3,t]} & p_{[1,4,t]} \\
p_{[2,1,t]} & p_{[2,2,t]} & p_{[2,3,t]} & p_{[2,4,t]} \\
p_{[3,1,t]} & p_{[3,2,t]} & p_{[3,3,t]} & p_{[3,4,t]} \\
p_{[4,1,t]} & p_{[4,2,t]} & p_{[4,3,t]} & p_{[4,4,t]}\\
\end{Bmatrix}
$$
Thus, 

$P4 = 1-P1-P2-P3$

$P1 = p\_live\_cvd*(1-p\_acvd\_cvdth)$

$P2 = p\_live\_cvdth + p\_live\_cvd*p\_acvd\_cvdth$ 

$P3 = p\_live\_oth\_death$

$P6= 1-(p\_ccvd\_cvdth+p\_ccvd\_acvd*p\_acvd\_cvdth)-p\_live\_oth\_death$

$P5= p\_ccvd\_cvdth+p\_ccvd\_acvd*p\_acvd\_cvdth$

# Strategy0
```{r, results='asis', message=FALSE}
noStrategy_data <- read_csv("data/Normal_data.csv")
print(xtable(data.frame(noStrategy_data),digits=c(0,0,0,0),
      caption = "Distribution of the population"),
      caption.placement="top",comment=FALSE)
```

```{r}
###################### Construct state-transition models for Strategy1 #####################
patient_group <- matrix(noStrategy_data$num, ncol=1,
                        dimnames=list(names_population))
result_m_M <- array(0, dim = c(10, 4, 14),
               dimnames = list(paste0("t",0:9), v_names_states, names_population))
# p_acvd_cvddth
p8 <-array(runif(140,min=0.02,max=0.1),dim=c(10,14),dimnames=list(1:10,names_population))
p9 <- array(NA, dim=c(10,14),dimnames=list(1:10,names_population))
p10 <- array(NA, dim=c(10,14), dimnames=list(1:10,names_population))

prob_CVD_group0 <- matrix(0, ncol=14, nrow=10,
                     dimnames=list(paste0("t",0:9),names_population))
prob_CVDlive_group0 <- matrix(0, ncol=14, nrow=10,
                     dimnames=list(paste0("t",0:9),names_population))

result_CVD <- matrix(0, ncol = 1, nrow = 14,
                     dimnames=list(names_population, ""))
result_CVDlive <- matrix(0, ncol = 1, nrow = 14,
                     dimnames=list(names_population, ""))
result_QALY <- matrix(0, ncol = 1, nrow = 14,
                     dimnames=list(names_population, ""))
result_Lifeyear <- matrix(0, ncol = 1, nrow = 14,
                     dimnames=list(names_population, ""))
result_CVDeath <- matrix(0, ncol = 1, nrow = 14,
                     dimnames=list(names_population, ""))
result_nonCVDeath <- matrix(0, ncol = 1, nrow = 14,
                     dimnames=list(names_population, ""))  
# create a matrix for p_acvd_cvdth 
for(i in 1:14){
  # construct a_P
  if(i == 7 | i == 14){
    a_P <- array(0, dim = c(n_states, n_states, 10),
               dimnames = list(v_names_states, v_names_states, 1:10))
    a_P["S1", "S1", 1:10] <- 1-(p_live_cvd[i]*(1-p8[1:10,i]) +
                               p_live_cvdth[i]*p_live_cvd[i]*p8[1:10,i] +
                               p_live_oth_death[i])
    a_P["S1", "S2", 1:10] <- p_live_cvd[i]*(1-p8[1:10,i])
    a_P["S1", "S3", 1:10] <- p_live_cvdth[i]*p_live_cvd[i]*p8[1:10,i]
    a_P["S1", "S4", 1:10] <- p_live_oth_death[i]
    a_P["S2", "S1", 1:10] <- 0
    a_P["S2", "S2", 1:10] <- 1-p_live_oth_death[i]-(p_ccvd_cvdth[i]+p_ccvd_acvd[i]*p8[1:10,i])
    a_P["S2", "S3", 1:10] <- p_ccvd_cvdth[i]+p_ccvd_acvd[i]*p8[1:10,i]
    a_P["S2", "S4", 1:10] <- p_live_oth_death[i]
    a_P["S3", "S3", 1:10] <- 1
    a_P["S4", "S4", 1:10] <- 1
    p9[1:10,i] <- p_ccvd_acvd[i]*(1-p8[1:10,i])
    p10[1:10,i] <- p_live_cvd[i]
  }

  if(i != 7 && i != 14){
    a_P <- array(0, dim = c(n_states, n_states, 10),
               dimnames = list(v_names_states, v_names_states, 1:10))
    a_P["S1", "S1", 1:5] <- 1-(p_live_cvd[i]*(1-p8[1:5,i]) +
                               p_live_cvdth[i]*p_live_cvd[i]*p8[1:5,i] +
                               p_live_oth_death[i])
    a_P["S1", "S2", 1:5] <- p_live_cvd[i]*(1-p8[1:5,i])
    a_P["S1", "S3", 1:5] <- p_live_cvdth[i]*p_live_cvd[i]*p8[1:5,i]
    a_P["S1", "S4", 1:5] <- p_live_oth_death[i]
    a_P["S2", "S1", 1:5] <- 0
    a_P["S2", "S2", 1:5] <- 1-p_live_oth_death[i]-
      (p_ccvd_cvdth[i]+p_ccvd_acvd[i]*p8[1:5,i])
    a_P["S2", "S3", 1:5] <- p_ccvd_cvdth[i]+
      p_ccvd_acvd[i]*p8[1:5,i]
    a_P["S2", "S4", 1:5] <- p_live_oth_death[i]
    a_P["S3", "S3", 1:5] <- 1
    a_P["S4", "S4", 1:5] <- 1
    a_P["S1", "S1", 6:10] <-  1-(p_live_cvd[i+1]*(1-p8[6:10,i+1])+
                             p_live_cvdth[i+1]*p_live_cvd[i+1]*p8[6:10,i+1]
                             +p_live_oth_death[i+1])
    a_P["S1", "S2", 6:10] <- p_live_cvd[i+1]*(1-p8[6:10,i+1])
    a_P["S1", "S3", 6:10] <- p_live_cvdth[i+1]*p_live_cvd[i+1]*p8[6:10,i+1]
    a_P["S1", "S4", 6:10] <- p_live_oth_death[i+1]
    a_P["S2", "S1", 6:10] <- 0
    a_P["S2", "S2", 6:10] <- 1-p_live_oth_death[i+1]-
       (p_ccvd_cvdth[i+1]+p_ccvd_acvd[i+1]*p8[6:10,i+1])
    a_P["S2", "S3", 6:10] <- p_ccvd_cvdth[i+1]+p_ccvd_acvd[i+1]*p8[6:10,i+1]
    a_P["S2", "S4", 6:10] <-  p_live_oth_death[i+1]
    a_P["S3", "S3", 6:10] <- 1
    a_P["S4", "S4", 6:10] <- 1
    p9[1:5,i] <- p_ccvd_acvd[i]*(1-p8[1:5,i])
    p9[6:10,i] <- p_ccvd_acvd[i+1]*(1-p8[6:10,i])
    p10[1:5,i] <- p_live_cvd[i]
    p10[6:10,i] <- p_live_cvd[i+1]
  }
  # construct m_M
    v_s_init <- c(state0 = 1, state1 = 0, state2 = 0, state3 = 0) 
    m_M <- matrix(0,nrow     = (n_t), ncol = n_states, 
                  dimnames = list(0:(n_t-1), v_names_states))
    m_M[1, ] <- v_s_init
    for(t in 1:9){
      m_M[t + 1, ] <- m_M[t, ] %*% a_P[, , t]
    }
  # calculate result
    prob_CVD_group0[ ,i] <- m_M[ ,1] * p10[ ,i]  # new occurence = S1*p10
    # new occurence = s1*p1+s2*p9
    prob_CVDlive_group0[ ,i] <- m_M[ ,1]*(a_P["S1", "S2", 1:10]) + m_M[ ,2]*p9[ ,i] 
    result_m_M[ , , i] <- m_M
  result_CVD[i] <- sum(prob_CVD_group0[, i] * patient_group[i])
  result_CVDlive[i] <- sum(prob_CVDlive_group0[, i] * patient_group[i])
  result_Lifeyear[i] <- sum(t(t(m_M) * year) * patient_group[i])
  result_QALY[i] <- sum(t(t(m_M) * uti_values)*patient_group[i] + 
                          prob_CVDlive_group0[, i]*out_trans_to_cvd*patient_group[i])
  result_CVDeath[i] <- m_M[10, 3] * patient_group[i]
  result_nonCVDeath[i] <- m_M[10, 4] * patient_group[i]
}
result_m_M[ , ,1] # an example for the patient group 40-45, male

```

### Result for Strategy0
```{r results='asis'}
result_CVD_stg0 <- sum(result_CVD)
print(xtable(data.frame(rbind(result_CVD,"sum" = result_CVD_stg0)),
             caption = "New CVD events for patients under Strategy0"),
      caption.placement="top",comment=FALSE)
print(xtable(data.frame(matrix(c(sum(result_CVD),sum(result_CVDeath),sum(result_nonCVDeath), 
                               sum(result_QALY),sum(result_Lifeyear)),nrow = 1, ncol=5,
                               dimnames = list("", c("CVD events","CVD Death","non-CVD Death",
                                                     "QALY", "Life Year")))),
             caption = "Result for Strategy0"), caption.placement="top",comment=FALSE)

```

\clearpage

```{r}
HR_l_stg1	<- 0.63
HR_m_stg1	<- 1.56
HR_h_stg1	<- 1.6

HR_l_stg2	<- 0.43
HR_m_stg2	<- 0.97
HR_h_stg2	<- 2.06

HR_l_stg3	<- 0.45
HR_m_stg3	<- 1.09
HR_h_stg3	<- 2.11
# lifestyle intervention for medium risk and above
HR_smk_cvd	<-	0.85
HR_smk_cvdth	<-	0.72
HR_salt_cvd	<-	0.81
HR_salt_cvdth	<-	0.66
HR_wtc_cvd	<-	0.93
HR_wtc_dth	<-	0.93
# treatment intervention for high risk (additional)
HR_hpt_lip_cvd	<-	0.7
HR_hpt_lip_cvdth <-	0.82
```
\begin{center}
\begin{table}
\caption{Incidence rate}
\begin{tabular}{cccc} 
\hline
Item & & CVD incidence(HR) & CVD cause-specific mortality (HR)  \\
\hline
\multirow{3}{6em}{Strategy 1}& {Low risk} & `r HR_l_stg1` & 1   \\
& {Medium risk}& `r HR_m_stg1`  &  1\\
& {High risk}& `r HR_h_stg1`  &  1.7 \\
\hline
\multirow{3}{6em}{Strategy 2}& {Low risk}& `r HR_l_stg2`  & 1 \\
& {Medium risk}  & `r HR_m_stg2` &  1\\
& {High risk}  &`r HR_h_stg2`  &  1.7\\
\hline
\multirow{3}{6em}{Strategy 3}& {Low risk}  & `r HR_l_stg3` & 1 \\
& {Medium risk}  & `r HR_m_stg3` &  1\\
& {High risk}  & `r HR_h_stg3` &  1.7\\
\hline
\multirow{3}{6em}{Intervention}& {Weight control}  & `r HR_wtc_cvd` &  `r HR_wtc_dth`\\
& {Smoke cession}  & `r HR_smk_cvd` & `r HR_smk_cvdth` \\
& {Salt reduction}  & `r HR_salt_cvd` & `r HR_salt_cvdth` \\
\hline
Medication & Statin and antihypertensive & `r HR_hpt_lip_cvd` &  `r HR_hpt_lip_cvdth` \\
\hline
\end{tabular}
\end{table}
\end{center}
# Strategy 1

```{r results='asis'}
print(xtable(data.frame(population_data[which(population_data$strategy == "strategy1"),]),digits=c(0,0,0,0,0,0,0),
      caption = "Distribution of the population under different strategies"),
      caption.placement="top",comment=FALSE)
```


```{r}
p_live_cvd_l <- ProbFactor(p_live_cvd,HR_l_stg1)
p_live_cvd_m <- ProbFactor(p_live_cvd,HR_m_stg1*
                             HR_smk_cvd*HR_salt_cvd*HR_wtc_cvd)  # lifestyle intervention
p_live_cvd_h <- ProbFactor(p_live_cvd,HR_h_stg1*
                             HR_smk_cvdth*HR_salt_cvdth*HR_wtc_dth*    # lifestyle intervention
                             HR_hpt_lip_cvdth)   # treatment intervention 
p_live_cvdth_l <- ProbFactor(p_live_cvdth,1)    # equal
p_live_cvdth_m <- ProbFactor(p_live_cvdth,1*
                               HR_smk_cvd*HR_salt_cvd*HR_wtc_cvd)  # lifestyle intervention 
p_live_cvdth_h <- ProbFactor(p_live_cvdth,1.7*
                               HR_smk_cvdth*HR_salt_cvdth*HR_wtc_dth* # lifestyle intervention
                               HR_hpt_lip_cvdth) # treatment intervention 
```

```{r}
risk_levels <- c("low","medium","high")
result_CVD_lmh <- matrix(0,  nrow = 14,ncol = 3,
                         dimnames = list(names_population, risk_levels))
p_live_cvd_lmh <- matrix(cbind(p_live_cvd_l,p_live_cvd_m,p_live_cvd_h), ncol=3,
                         dimnames = list(names_population,risk_levels))
p_live_cvdth_lmh <- matrix(cbind(p_live_cvdth_l,p_live_cvdth_m,p_live_cvdth_h), ncol=3,
                           dimnames = list(names_population,risk_levels))
patient_group <- matrix(cbind(population_data[which(population_data$strategy=="strategy1"),]$low,
                              population_data[which(population_data$strategy=="strategy1"),]$medium,
                              population_data[which(population_data$strategy=="strategy1"),]$high),
       ncol = 3, nrow=14,dimnames = list(names_population,risk_levels))
prob_CVD_group1 <- matrix(0, ncol=14, nrow=10,
                     dimnames=list(paste0("t",0:9),names_population))
prob_CVDlive_group1 <- matrix(0, ncol=14, nrow=10,
                     dimnames=list(paste0("t",0:9),names_population))
result_CVD_stg1 <- matrix(0, ncol = 3, nrow = 14,
                     dimnames=list(names_population, risk_levels))
result_CVDlive_stg1 <- matrix(0, ncol = 3, nrow = 14,
                     dimnames=list(names_population, risk_levels))
result_QALY_stg1 <- matrix(0, ncol = 3, nrow = 14,
                     dimnames=list(names_population, risk_levels))
result_Lifeyear_stg1 <- matrix(0, ncol = 3, nrow = 14,
                     dimnames=list(names_population, risk_levels))
result_CVDeath_stg1 <- matrix(0, ncol = 3, nrow = 14,
                     dimnames=list(names_population, risk_levels))
result_nonCVDeath_stg1 <- matrix(0, ncol = 3, nrow = 14,
                     dimnames=list(names_population, risk_levels))

p8 <-array(runif(140,min=0.02,max=0.1),dim=c(10,14),dimnames=list(1:10,names_population))
p9 <- array(NA, dim=c(10,14),dimnames=list(1:10,names_population))
p10 <- array(NA, dim=c(10,14), dimnames=list(1:10,names_population))

for(r in 1:3){  # three rish groups
  # create a matrix for p_acvd_cvdth 
  for(i in 1:14){
  # construct a_P
 if(i == 7 | i == 14){
    a_P <- array(0, dim = c(n_states, n_states, 10),
               dimnames = list(v_names_states, v_names_states, 1:10))
    a_P["S1", "S1", 1:10] <- 1-(p_live_cvd_lmh[i,r]*(1-p8[1:10,i]) +
                               p_live_cvdth_lmh[i,r]*p_live_cvd_lmh[i,r]*(1-p8[1:10,i]) +
                               p_live_oth_death[i])
    a_P["S1", "S2", 1:10] <- p_live_cvd_lmh[i,r]*(1-(1-p8[1:10,i]))
    a_P["S1", "S3", 1:10] <- p_live_cvdth_lmh[i,r]*p_live_cvd_lmh[i,r]*(1-p8[1:10,i]) 
    a_P["S1", "S4", 1:10] <- p_live_oth_death[i]  
    a_P["S2", "S1", 1:10] <- 0
    a_P["S2", "S2", 1:10] <- 1-p_live_oth_death[i]-
      (p_ccvd_cvdth[i]+p_ccvd_acvd[i]*(1-p8[1:10,i]))
    a_P["S2", "S3", 1:10] <- p_ccvd_cvdth[i]+
      p_ccvd_acvd[i]*(1-p8[1:10,i]) 
    a_P["S2", "S4", 1:10] <- p_live_oth_death[i]
    a_P["S3", "S3", 1:10] <- 1
    a_P["S4", "S4", 1:10] <- 1
    p9[1:10,i] <- p_ccvd_acvd[i]*(1-p8[1:10,i])
    p10[1:10,i] <- p_live_cvd[i]
  }
  if(i != 7 && i != 14){
    a_P <- array(0, dim = c(n_states, n_states, 10),
               dimnames = list(v_names_states, v_names_states, 1:10))
    a_P["S1", "S1", 1:5] <- 1-(p_live_cvd_lmh[i,r]*(1-p8[1:5,i]) +
                               p_live_cvdth_lmh[i,r]*p_live_cvd_lmh[i,r]*p8[1:5,i] +
                               p_live_oth_death[i])
    a_P["S1", "S2", 1:5] <- p_live_cvd_lmh[i,r]*(1-p8[1:5,i])
    a_P["S1", "S3", 1:5] <- p_live_cvdth_lmh[i,r]*p_live_cvd_lmh[i,r]*p8[1:5,i]
    a_P["S1", "S4", 1:5] <- p_live_oth_death[i]
    a_P["S2", "S1", 1:5] <- 0
    a_P["S2", "S2", 1:5] <- 1-p_live_oth_death[i]-
      (p_ccvd_cvdth[i]+p_ccvd_acvd[i]*p8[1:5,i])
    a_P["S2", "S3", 1:5] <- p_ccvd_cvdth[i]+
      p_ccvd_acvd[i]*p8[1:5,i]
    a_P["S2", "S4", 1:5] <- p_live_oth_death[i]
    a_P["S3", "S3", 1:5] <- 1
    a_P["S4", "S4", 1:5] <- 1
    a_P["S1", "S1", 6:10] <-  1-(p_live_cvd_lmh[i+1,r]*(1-p8[1:5,i+1])+
                             p_live_cvdth_lmh[i+1,r]*p_live_cvd_lmh[i+1,r]*p8[1:5,i+1]
                             +p_live_oth_death[i+1])
    a_P["S1", "S2", 6:10] <- p_live_cvd_lmh[i+1,r]*(1-p8[1:5,i+1])
    a_P["S1", "S3", 6:10] <- p_live_cvdth_lmh[i+1,r]*p_live_cvd_lmh[i+1,r]*p8[1:5,i+1]
    a_P["S1", "S4", 6:10] <- p_live_oth_death[i+1]
    a_P["S2", "S1", 6:10] <- 0
    a_P["S2", "S2", 6:10] <- 1-p_live_oth_death[i+1]-
       (p_ccvd_cvdth[i+1]+p_ccvd_acvd[i+1] * p8[1:5,i+1])
    a_P["S2", "S3", 6:10] <- p_ccvd_cvdth[i+1]+p_ccvd_acvd[i+1]*p8[1:5,i+1]
    a_P["S2", "S4", 6:10] <-  p_live_oth_death[i+1]
    a_P["S3", "S3", 6:10] <- 1
    a_P["S4", "S4", 6:10] <- 1
    p9[1:5,i] <- p_ccvd_acvd[i]*(1-p8[1:5,i])
    p9[6:10,i] <- p_ccvd_acvd[i+1]*(1-p8[6:10,i])
    p10[1:5,i] <- p_live_cvd[i]
    p10[6:10,i] <- p_live_cvd[i+1]
  }
     # construct m_M
    v_s_init <- c(state0 = 1, state1 = 0, state2 = 0, state3 = 0) 
    m_M <- matrix(0,nrow     = (n_t), ncol = n_states, 
                  dimnames = list(0:(n_t-1), v_names_states))
    m_M[1, ] <- v_s_init
    for(t in 1:9){
      m_M[t + 1, ] <- m_M[t, ] %*% a_P[, , t]
    }
    # calculate result
    prob_CVD_group1[ ,i] <- m_M[ ,1]* p10[ ,i]  # new occurence = S1*p9
    prob_CVDlive_group1[ ,i] <- m_M[ ,1]*(a_P["S1", "S2", 1:10]) + m_M[ ,2]*p9[ ,i] # new occurence = s1*p1+s2*p9
  
  result_CVD_stg1[i,r] <- sum(prob_CVD_group1[,i]*patient_group[i,r])
  result_CVDlive_stg1[i,r] <- sum(prob_CVDlive_group1[,i]*patient_group[i,r])
  result_Lifeyear_stg1[i,r] <- sum(t( t(m_M) * year )*patient_group[i,r])
  
  result_QALY_stg1[i,r] <- sum(t(t(m_M) * uti_values)*patient_group[i,r] + 
                          prob_CVDlive_group1[, i]*out_trans_to_cvd*patient_group[i,r])
  result_CVDeath_stg1[i,r] <- m_M[10,3]*patient_group[i,r]
  result_nonCVDeath_stg1[i,r] <- m_M[10,4]*patient_group[i,r]
}
}

```
### Result for Strategy1
```{r results="asis"}
print(xtable((rbind(result_CVD_stg1, "sum" = colSums(result_CVD_stg1))),
      caption = "New CVD events for patients under Strategy1"),
      caption.placement="top",comment=FALSE)
result_tab <- data.frame(matrix(c(sum(result_CVD_stg1),sum(result_CVDeath_stg1),
                                  sum(result_nonCVDeath_stg1), sum(result_QALY_stg1),
                                  sum(result_Lifeyear_stg1)),nrow = 1, ncol=5,
                     dimnames = list("", c("CVD events","CVD Death","non-CVD Death",
                                           "QALY", "Life Year"))))
print(xtable(data.frame(result_tab),
      caption = "Result for Strategy1"),
      caption.placement="top",comment=FALSE)
```

\clearpage
# Strategy 2

```{r results="asis"}
print(xtable(data.frame(population_data[which(population_data$strategy == "strategy2"),]),digits=c(0,0,0,0,0,0,0),
      caption = "Distribution of the population under different strategies"),
      caption.placement="top",comment=FALSE)
```


```{r}
p_live_cvd_l <- ProbFactor(p_live_cvd,HR_l_stg2)
p_live_cvd_m <- ProbFactor(p_live_cvd,HR_m_stg2*
                             HR_smk_cvd*HR_salt_cvd*HR_wtc_cvd)  # lifestyle intervention
p_live_cvd_h <- ProbFactor(p_live_cvd,HR_h_stg2*
                             HR_smk_cvdth*HR_salt_cvdth*HR_wtc_dth*    # lifestyle intervention
                             HR_hpt_lip_cvdth)   # treatment intervention 
p_live_cvdth_l <- ProbFactor(p_live_cvdth,1)    # equal
p_live_cvdth_m <- ProbFactor(p_live_cvdth,1*
                               HR_smk_cvd*HR_salt_cvd*HR_wtc_cvd)  # lifestyle intervention 
p_live_cvdth_h <- ProbFactor(p_live_cvdth,1.7*
                               HR_smk_cvdth*HR_salt_cvdth*HR_wtc_dth* # lifestyle intervention
                               HR_hpt_lip_cvdth) # treatment intervention 
```

```{r}
risk_levels <- c("low","medium","high")
result_CVD_lmh <- matrix(0,  nrow = 14,ncol = 3,
                         dimnames = list(names_population, risk_levels))
p_live_cvd_lmh <- matrix(cbind(p_live_cvd_l,p_live_cvd_m,p_live_cvd_h), ncol=3,
                         dimnames = list(names_population,risk_levels))
p_live_cvdth_lmh <- matrix(cbind(p_live_cvdth_l,p_live_cvdth_m,p_live_cvdth_h), ncol=3,
                           dimnames = list(names_population,risk_levels))
patient_group <- matrix(cbind(population_data[which(population_data$strategy=="strategy2"),]$low,
                              population_data[which(population_data$strategy=="strategy2"),]$medium,
                              population_data[which(population_data$strategy=="strategy2"),]$high),
       ncol = 3, nrow=14,dimnames = list(names_population,risk_levels))
prob_CVD_group2 <- matrix(0, ncol=14, nrow=10,
                     dimnames=list(paste0("t",0:9),names_population))
prob_CVDlive_group2 <- matrix(0, ncol=14, nrow=10,
                     dimnames=list(paste0("t",0:9),names_population))
result_CVD_stg2 <- matrix(0, ncol = 3, nrow = 14,
                     dimnames=list(names_population, risk_levels))
result_CVDlive_stg2 <- matrix(0, ncol = 3, nrow = 14,
                     dimnames=list(names_population, risk_levels))
result_QALY_stg2 <- matrix(0, ncol = 3, nrow = 14,
                     dimnames=list(names_population, risk_levels))
result_Lifeyear_stg2 <- matrix(0, ncol = 3, nrow = 14,
                     dimnames=list(names_population, risk_levels))
result_CVDeath_stg2 <- matrix(0, ncol = 3, nrow = 14,
                     dimnames=list(names_population, risk_levels))
result_nonCVDeath_stg2 <- matrix(0, ncol = 3, nrow = 14,
                     dimnames=list(names_population, risk_levels)) 
p8 <-array(runif(140,min=0.02,max=0.1),dim=c(10,14),dimnames=list(1:10,names_population))
p9 <- array(NA, dim=c(10,14),dimnames=list(1:10,names_population))
p10 <- array(NA, dim=c(10,14), dimnames=list(1:10,names_population))
for(r in 1:3){  # three rish groups
  # create a matrix for p_acvd_cvdth 
  for(i in 1:14){
  # construct a_P
  if(i == 7 | i == 14){
    a_P <- array(0, dim = c(n_states, n_states, 10),
               dimnames = list(v_names_states, v_names_states, 1:10))
    a_P["S1", "S1", 1:10] <- 1-(p_live_cvd_lmh[i,r]*(1-p8[1:10,i]) +
                               p_live_cvdth_lmh[i,r]*p_live_cvd_lmh[i,r]*(1-p8[1:10,i]) +
                               p_live_oth_death[i])
    a_P["S1", "S2", 1:10] <- p_live_cvd_lmh[i,r]*(1-(1-p8[1:10,i]))
    a_P["S1", "S3", 1:10] <- p_live_cvdth_lmh[i,r]*p_live_cvd_lmh[i,r]*(1-p8[1:10,i]) 
    a_P["S1", "S4", 1:10] <- p_live_oth_death[i]  
    a_P["S2", "S1", 1:10] <- 0
    a_P["S2", "S2", 1:10] <- 1-p_live_oth_death[i]-
      (p_ccvd_cvdth[i]+p_ccvd_acvd[i]*(1-p8[1:10,i]))
    a_P["S2", "S3", 1:10] <- p_ccvd_cvdth[i]+
      p_ccvd_acvd[i]*(1-p8[1:10,i]) 
    a_P["S2", "S4", 1:10] <- p_live_oth_death[i]
    a_P["S3", "S3", 1:10] <- 1
    a_P["S4", "S4", 1:10] <- 1
    p9[1:10,i] <- p_ccvd_acvd[i]*(1-p8[1:10,i])
    p10[1:10,i] <- p_live_cvd[i]
  }
  if(i != 7 && i != 14){
    a_P <- array(0, dim = c(n_states, n_states, 10),
               dimnames = list(v_names_states, v_names_states, 1:10))
    a_P["S1", "S1", 1:5] <- 1-(p_live_cvd_lmh[i,r]*(1-p8[1:5,i]) +
                               p_live_cvdth_lmh[i,r]*p_live_cvd_lmh[i,r]*p8[1:5,i] +
                               p_live_oth_death[i])
    a_P["S1", "S2", 1:5] <- p_live_cvd_lmh[i,r]*(1-p8[1:5,i])
    a_P["S1", "S3", 1:5] <- p_live_cvdth_lmh[i,r]*p_live_cvd_lmh[i,r]*p8[1:5,i]
    a_P["S1", "S4", 1:5] <- p_live_oth_death[i]
    a_P["S2", "S1", 1:5] <- 0
    a_P["S2", "S2", 1:5] <- 1-p_live_oth_death[i]-
      (p_ccvd_cvdth[i]+p_ccvd_acvd[i]*p8[1:5,i])
    a_P["S2", "S3", 1:5] <- p_ccvd_cvdth[i]+
      p_ccvd_acvd[i]*p8[1:5,i]
    a_P["S2", "S4", 1:5] <- p_live_oth_death[i]
    a_P["S3", "S3", 1:5] <- 1
    a_P["S4", "S4", 1:5] <- 1
    a_P["S1", "S1", 6:10] <-  1-(p_live_cvd_lmh[i+1,r]*(1-p8[1:5,i+1])+
                             p_live_cvdth_lmh[i+1,r]*p_live_cvd_lmh[i+1,r]*p8[1:5,i+1]
                             +p_live_oth_death[i+1])
    a_P["S1", "S2", 6:10] <- p_live_cvd_lmh[i+1,r]*(1-p8[1:5,i+1])
    a_P["S1", "S3", 6:10] <- p_live_cvdth_lmh[i+1,r]*p_live_cvd_lmh[i+1,r]*p8[1:5,i+1]
    a_P["S1", "S4", 6:10] <- p_live_oth_death[i+1]
    a_P["S2", "S1", 6:10] <- 0
    a_P["S2", "S2", 6:10] <- 1-p_live_oth_death[i+1]-
       (p_ccvd_cvdth[i+1]+p_ccvd_acvd[i+1]*p8[1:5,i+1])
    a_P["S2", "S3", 6:10] <- p_ccvd_cvdth[i+1]+p_ccvd_acvd[i+1]*p8[1:5,i+1]
    a_P["S2", "S4", 6:10] <-  p_live_oth_death[i+1]
    a_P["S3", "S3", 6:10] <- 1
    a_P["S4", "S4", 6:10] <- 1
    p9[1:5,i] <- p_ccvd_acvd[i]*(1-p8[1:5,i])
    p9[6:10,i] <- p_ccvd_acvd[i+1]*(1-p8[6:10,i])
    p10[1:5,i] <- p_live_cvd[i]
    p10[6:10,i] <- p_live_cvd[i+1]
  }
     # construct m_M
    v_s_init <- c(state0 = 1, state1 = 0, state2 = 0, state3 = 0) 
    m_M <- matrix(0,nrow     = (n_t), ncol = n_states, 
                  dimnames = list(0:(n_t-1), v_names_states))
    m_M[1, ] <- v_s_init
    for(t in 1:9){
      m_M[t + 1, ] <- m_M[t, ] %*% a_P[, , t]
    }
    # calculate result
    prob_CVD_group2[ ,i] <- m_M[ ,1]* p10[ ,i]  # new occurence = S1*p9
    prob_CVDlive_group2[ ,i] <- m_M[ ,1]*(a_P["S1", "S2", 1:10]) + m_M[ ,2]*p9[ ,i] 
  result_CVD_stg2[i,r] <- sum(prob_CVD_group2[,i]*patient_group[i,r])
  result_CVDlive_stg2[i,r] <- sum(prob_CVDlive_group2[,i]*patient_group[i,r])
  result_Lifeyear_stg2[i,r] <- sum(t( t(m_M) * year )*patient_group[i,r])
  
  result_QALY_stg2[i,r] <- sum(t(t(m_M) * uti_values)*patient_group[i,r] + 
                          prob_CVDlive_group2[, i]*out_trans_to_cvd*patient_group[i,r])
  result_CVDeath_stg2[i,r] <- m_M[10,3]*patient_group[i,r]
  result_nonCVDeath_stg2[i,r] <- m_M[10,4]*patient_group[i,r]
}}

```
### Result for Strategy2
```{r results="asis"}
print(xtable((rbind(result_CVD_stg2, "sum" = colSums(result_CVD_stg2))),
      caption = "New CVD events for patients under Strategy1"),
      caption.placement="top",comment=FALSE)
result_tab <- data.frame(matrix(c(sum(result_CVD_stg2),sum(result_CVDeath_stg2),
                                  sum(result_nonCVDeath_stg2),sum(result_QALY_stg2),
                                  sum(result_Lifeyear_stg2)), nrow = 1, ncol=5,
                     dimnames = list("", c("CVD events","CVD Death","non-CVD Death",
                                           "QALY", "Life Year"))))
print(xtable(data.frame(result_tab),caption = "Result for Strategy2"),
      caption.placement="top",comment=FALSE)
```

\clearpage
# Strategy 3


```{r results="asis"}
print(xtable(data.frame(population_data[which(population_data$strategy == "strategy3"),]),digits=c(0,0,0,0,0,0,0),
      caption = "Distribution of the population under different strategies"),
      caption.placement="top",comment=FALSE)
```


```{r}
p_live_cvd_l <- ProbFactor(p_live_cvd,HR_l_stg3)
p_live_cvd_m <- ProbFactor(p_live_cvd,HR_m_stg3*
                             HR_smk_cvd*HR_salt_cvd*HR_wtc_cvd)  # lifestyle intervention
p_live_cvd_h <- ProbFactor(p_live_cvd,HR_h_stg3*
                             HR_smk_cvdth*HR_salt_cvdth*HR_wtc_dth*    # lifestyle intervention
                             HR_hpt_lip_cvdth)   # treatment intervention 
p_live_cvdth_l <- ProbFactor(p_live_cvdth,1)    # equal
p_live_cvdth_m <- ProbFactor(p_live_cvdth,1*
                               HR_smk_cvd*HR_salt_cvd*HR_wtc_cvd)  # lifestyle intervention 
p_live_cvdth_h <- ProbFactor(p_live_cvdth,1.7*
                               HR_smk_cvdth*HR_salt_cvdth*HR_wtc_dth* # lifestyle intervention
                               HR_hpt_lip_cvdth) # treatment intervention 
```

```{r}
risk_levels <- c("low","medium","high")
result_CVD_lmh <- matrix(0,  nrow = 14,ncol = 3,
                         dimnames = list(names_population, risk_levels))
p_live_cvd_lmh <- matrix(cbind(p_live_cvd_l,p_live_cvd_m,p_live_cvd_h), ncol=3,
                         dimnames = list(names_population,risk_levels))
p_live_cvdth_lmh <- matrix(cbind(p_live_cvdth_l,p_live_cvdth_m,p_live_cvdth_h), ncol=3,
                           dimnames = list(names_population,risk_levels))
patient_group <- matrix(cbind(population_data[which(population_data$strategy=="strategy3"),]$low,
                              population_data[which(population_data$strategy=="strategy3"),]$medium,
                              population_data[which(population_data$strategy=="strategy3"),]$high),
       ncol = 3, nrow=14,dimnames = list(names_population,risk_levels))
prob_CVD_group3 <- matrix(0, ncol=14, nrow=10,
                     dimnames=list(paste0("t",0:9),names_population))
prob_CVDlive_group3 <- matrix(0, ncol=14, nrow=10,
                     dimnames=list(paste0("t",0:9),names_population))
result_CVD_stg3 <- matrix(0, ncol = 3, nrow = 14,
                     dimnames=list(names_population, risk_levels))
result_CVDlive_stg3 <- matrix(0, ncol = 3, nrow = 14,
                     dimnames=list(names_population, risk_levels))
result_QALY_stg3 <- matrix(0, ncol = 3, nrow = 14,
                     dimnames=list(names_population, risk_levels))
result_Lifeyear_stg3 <- matrix(0, ncol = 3, nrow = 14,
                     dimnames=list(names_population, risk_levels))
result_CVDeath_stg3 <- matrix(0, ncol = 3, nrow = 14,
                     dimnames=list(names_population, risk_levels))
result_nonCVDeath_stg3 <- matrix(0, ncol = 3, nrow = 14,
                     dimnames=list(names_population, risk_levels)) 

p8 <-array(runif(140,min=0.02,max=0.1),dim=c(10,14),dimnames=list(1:10,names_population))
p9 <- array(NA, dim=c(10,14),dimnames=list(1:10,names_population))
p10 <- array(NA, dim=c(10,14), dimnames=list(1:10,names_population))
for(r in 1:3){  # three rish groups
  # create a matrix for p_acvd_cvdth 
  for(i in 1:14){
  # construct a_P
 if(i == 7 | i == 14){
    a_P <- array(0, dim = c(n_states, n_states, 10),
               dimnames = list(v_names_states, v_names_states, 1:10))
    a_P["S1", "S1", 1:10] <- 1-(p_live_cvd_lmh[i,r]*(1-p8[1:10,i]) +
                               p_live_cvdth_lmh[i,r]*p_live_cvd_lmh[i,r]*(1-p8[1:10,i]) +
                               p_live_oth_death[i])
    a_P["S1", "S2", 1:10] <- p_live_cvd_lmh[i,r]*(1-(1-p8[1:10,i]))
    a_P["S1", "S3", 1:10] <- p_live_cvdth_lmh[i,r]*p_live_cvd_lmh[i,r]*(1-p8[1:10,i]) 
    a_P["S1", "S4", 1:10] <- p_live_oth_death[i]  
    a_P["S2", "S1", 1:10] <- 0
    a_P["S2", "S2", 1:10] <- 1-p_live_oth_death[i]-
      (p_ccvd_cvdth[i]+p_ccvd_acvd[i]*(1-p8[1:10,i]))
    a_P["S2", "S3", 1:10] <- p_ccvd_cvdth[i]+
      p_ccvd_acvd[i]*(1-p8[1:10,i]) 
    a_P["S2", "S4", 1:10] <- p_live_oth_death[i]
    a_P["S3", "S3", 1:10] <- 1
    a_P["S4", "S4", 1:10] <- 1
    p9[1:10,i] <- p_ccvd_acvd[i]*(1-p8[1:10,i])
    p10[1:10,i] <- p_live_cvd[i]
  }
  if(i != 7 && i != 14){
    a_P <- array(0, dim = c(n_states, n_states, 10),
               dimnames = list(v_names_states, v_names_states, 1:10))
    a_P["S1", "S1", 1:5] <- 1-(p_live_cvd_lmh[i,r]*(1-p8[1:5,i]) +
                               p_live_cvdth_lmh[i,r]*p_live_cvd_lmh[i,r]*p8[1:5,i] +
                               p_live_oth_death[i])
    a_P["S1", "S2", 1:5] <- p_live_cvd_lmh[i,r]*(1-p8[1:5,i])
    a_P["S1", "S3", 1:5] <- p_live_cvdth_lmh[i,r]*p_live_cvd_lmh[i,r]*p8[1:5,i]
    a_P["S1", "S4", 1:5] <- p_live_oth_death[i]
    a_P["S2", "S1", 1:5] <- 0
    a_P["S2", "S2", 1:5] <- 1-p_live_oth_death[i]-
      (p_ccvd_cvdth[i]+p_ccvd_acvd[i]*p8[1:5,i])
    a_P["S2", "S3", 1:5] <- p_ccvd_cvdth[i]+
      p_ccvd_acvd[i]*p8[1:5,i]
    a_P["S2", "S4", 1:5] <- p_live_oth_death[i]
    a_P["S3", "S3", 1:5] <- 1
    a_P["S4", "S4", 1:5] <- 1
    a_P["S1", "S1", 6:10] <-  1-(p_live_cvd_lmh[i+1,r]*(1-p8[1:5,i+1])+
                             p_live_cvdth_lmh[i+1,r]*p_live_cvd_lmh[i+1,r]*p8[1:5,i+1]
                             +p_live_oth_death[i+1])
    a_P["S1", "S2", 6:10] <- p_live_cvd_lmh[i+1,r]*(1-p8[1:5,i+1])
    a_P["S1", "S3", 6:10] <- p_live_cvdth_lmh[i+1,r]*p_live_cvd_lmh[i+1,r]*p8[1:5,i+1]
    a_P["S1", "S4", 6:10] <- p_live_oth_death[i+1]
    a_P["S2", "S1", 6:10] <- 0
    a_P["S2", "S2", 6:10] <- 1-p_live_oth_death[i+1]-
       (p_ccvd_cvdth[i+1]+p_ccvd_acvd[i+1]*p8[1:5,i+1])
    a_P["S2", "S3", 6:10] <- p_ccvd_cvdth[i+1]+p_ccvd_acvd[i+1]*p8[1:5,i+1]
    a_P["S2", "S4", 6:10] <-  p_live_oth_death[i+1]
    a_P["S3", "S3", 6:10] <- 1
    a_P["S4", "S4", 6:10] <- 1
    p9[1:5,i] <- p_ccvd_acvd[i]*(1-p8[1:5,i])
    p9[6:10,i] <- p_ccvd_acvd[i+1]*(1-p8[6:10,i])
    p10[1:5,i] <- p_live_cvd[i]
    p10[6:10,i] <- p_live_cvd[i+1]
  }
     # construct m_M
    v_s_init <- c(state0 = 1, state1 = 0, state2 = 0, state3 = 0) 
    m_M <- matrix(0,nrow     = (n_t), ncol = n_states, 
                  dimnames = list(0:(n_t-1), v_names_states))
    m_M[1, ] <- v_s_init
    for(t in 1:9){
      m_M[t + 1, ] <- m_M[t, ] %*% a_P[, , t]
    }
     # calculate result
    prob_CVD_group3[ ,i] <- m_M[ ,1]* p10[ ,i]  # new occurence = S1*p9
    prob_CVDlive_group3[ ,i] <- m_M[ ,1]*(a_P["S1", "S2", 1:10]) + m_M[ ,2]*p9[ ,i] 
  result_CVD_stg3[i,r] <- sum(prob_CVD_group3[,i]*patient_group[i,r])
  result_CVDlive_stg3[i,r] <- sum(prob_CVDlive_group3[,i]*patient_group[i,r])
  result_Lifeyear_stg3[i,r] <- sum(t( t(m_M) * year )*patient_group[i,r])
  
  result_QALY_stg3[i,r] <- sum(t(t(m_M) * uti_values)*patient_group[i,r] + 
                          prob_CVDlive_group3[, i]*out_trans_to_cvd*patient_group[i,r])
  result_CVDeath_stg3[i,r] <- m_M[10,3]*patient_group[i,r]
  result_nonCVDeath_stg3[i,r] <- m_M[10,4]*patient_group[i,r]
}
}
```


```{r}
# There is another group for Strategy3
noncreen_names <- c("m40","m45","f40","f45")
noscreen_group <- matrix(c(229,498,444,856),ncol = 1, nrow = 4,
                         dimnames = list(noncreen_names,""))
noscreen_group_CVD <- matrix(NA,ncol = 1, nrow = 4,
                             dimnames = list(noncreen_names,""))
noscreen_group_CVDlive <- matrix(NA,ncol = 1, nrow = 4,
                             dimnames = list(noncreen_names,""))
noscreen_group_Lifeyear <- matrix(NA,ncol = 1, nrow = 4,
                             dimnames = list(noncreen_names,""))
noscreen_group_QALY <- matrix(NA,ncol = 1, nrow = 4,
                             dimnames = list(noncreen_names,""))
noscreen_group_CVDeath <- matrix(NA,ncol = 1, nrow = 4,
                             dimnames = list(noncreen_names,""))
noscreen_group_nonCVDeath <- matrix(NA,ncol = 1, nrow = 4,
                             dimnames = list(noncreen_names,""))
m_M1 <- result_m_M[ , , 1]
m_M2 <- result_m_M[ , , 2]
m_M3 <- result_m_M[ , , 7]
m_M4 <- result_m_M[ , , 8]
noscreen_m_M <- list(m_M1, m_M2, m_M3, m_M4)

for(i in 1:4){
  name <- noncreen_names[i]
  noscreen_group_CVD[i] <- sum(prob_CVD_group0[,noncreen_names][,i] * noscreen_group[i])
  noscreen_group_Lifeyear[i] <- sum(t(t(result_m_M[,,name]) * year)  * noscreen_group[i])
  noscreen_group_QALY[i] <- sum(t(t(result_m_M[,,name]) * uti_values)*noscreen_group[i] + 
                          prob_CVDlive_group0[, i]*out_trans_to_cvd*noscreen_group[i])
  noscreen_group_CVDeath[i] <- sum(data.frame(noscreen_m_M[i])[10,3]*noscreen_group[i])
  noscreen_group_nonCVDeath[i] <-  sum(data.frame(noscreen_m_M[i])[10,4]*noscreen_group[i])
}


```
### Result for Strategy3
```{r results="asis"}
print(xtable((rbind(result_CVD_stg3, "sum" = colSums(result_CVD_stg3))),
      caption = "New CVD events for patients under Strategy1"),
      caption.placement="top",comment=FALSE)


result_CVD_stg3 <- sum(result_CVD_stg3, noscreen_group_CVD)

result_CVDlive_stg3 <- sum(result_CVDlive_stg3, noscreen_group_CVDlive)
result_Lifeyear_stg3 <- sum(result_Lifeyear_stg3, noscreen_group_Lifeyear)
result_QALY_stg3 <- sum(result_QALY_stg3, noscreen_group_QALY)
result_CVDeath_stg3 <- sum(result_CVDeath_stg3, noscreen_group_CVDeath)
result_nonCVDeath_stg3 <- sum(result_nonCVDeath_stg3, noscreen_group_nonCVDeath) 

result_tab <- data.frame(matrix(c(sum(result_CVD_stg3),sum(result_CVDeath_stg3),
                                  sum(result_nonCVDeath_stg3),
                                  sum(result_QALY_stg3),
                                  sum(result_Lifeyear_stg3)), nrow = 1, ncol=5,
                     dimnames = list("", c("CVD events","CVD Death","non-CVD Death",
                                           "QALY", "Life Year"))))
print(xtable(data.frame(result_tab),
      caption = "Result for Strategy3"),
      caption.placement="top",comment=FALSE)
```

# Conclusion

```{r results="asis"}

print(xtable((matrix(cbind(sum(result_CVD),sum(result_CVD_stg1),
                           sum(result_CVD_stg2),sum(result_CVD_stg3)),nrow = 1, ncol = 4,
      dimnames = list("",v_names_str))),
      caption = "CVD events for patients under 3 strategies"),
      caption.placement="top",comment=FALSE)

```

```{r results="asis"}
print(xtable((matrix(cbind(sum(result_QALY),sum(result_QALY_stg1),
                           sum(result_QALY_stg2),sum(result_QALY_stg3)),nrow = 1, ncol = 4,
      dimnames = list("",v_names_str))),
      caption = "QALY for patients under 3 strategies"),
      caption.placement="top",comment=FALSE)

```

```{r results="asis"}
print(xtable((matrix(cbind(sum(result_Lifeyear),sum(result_Lifeyear_stg1),
                           sum(result_Lifeyear_stg2),sum(result_Lifeyear_stg3)),nrow = 1, ncol = 4,
      dimnames = list("",v_names_str))),
      caption = "Life year for patients under 3 strategies"),
      caption.placement="top",comment=FALSE)

```
