---
title: "Report for the Markov model (cohort state-transition model)"
header-includes:
   - \usepackage{amsmath}
   - \usepackage{booktabs}
   - \usepackage{fancyhdr}
   - \pagestyle{fancy}
   - \usepackage{array}
   - \usepackage{multirow}
   # - \usepackage{afterpage}
   - \usepackage{rotating}
output: pdf_document
# classoption: landscape
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(xtable)
library(darthtools)
library(ggplot2)
library(readr)
source("function/transform_func.R")
```
# Data and parameters
```{r, results='asis', message=FALSE}
rate_data <- read_csv("data/ghdx_data.csv")
```

```{r, results='asis', message=FALSE}
noStrategy_data <- read_csv("data/Normal_data.csv")
```

```{r, results='asis', message=FALSE}
population_data <- read_csv("data/Normal3Stra_data.csv")
population_data <- data.frame(population_data)
```

\clearpage
```{r}
n_t <- 10   # time horizon, number of cycles
v_names_states <- c("S1", "S2", "S3", "S4") # S1: live; S2: cvd; S3: cvdth; S4: oth_death 
n_states    <- length(v_names_states)   # number of health states 
v_names_str <- c("Strategy0","Strategy1", "Strategy2", "Strategy3") # store the strategy names
n_str       <- length(v_names_str)      # number of strategies

# Health utilities
out_cvd_free <-	1   # utility when being S1
out_cvd <- 0.9   # utility when being S2
out_dth <-	0   # utility when being S3 and S4 together
out_trans_to_cvd <-	-0.038    # TODO

uti_values <- c(out_cvd_free, out_cvd, out_dth, out_dth)
year <- c(1,1,0,0)

HR_cvdhistory_cvd <-	1.37
HR_cvdhistory_cvdth <- 3.12
HR_high_live_cvdth <-	1.17

p_live_oth_death <- rate_to_prob(r=rate_data$death_nonCVD,t = 1)
p_live_cvd <- rate_to_prob(r=rate_data$incidence, t=1)
p_live_cvdth <- rate_to_prob(r=rate_data$death_CVD, t=1)
# transition probability from S2 to S3
p_ccvd_acvd <- rate_to_prob(rate_data$incidence*HR_cvdhistory_cvd, t=1)
p_ccvd_cvdth <- rate_to_prob(rate_data$death_CVD*HR_cvdhistory_cvdth,t=1)

set.seed(1)
p_acvd_cvdth <- matrix(NA)
for(i in 1:length(p_live_cvd)){
  p_acvd_cvdth[i] <- runif(1,min=0.02,max=0.1)
}

# half-cycle correction could be added
```

# Strategy 0

```{r}
###################### Construct state-transition models for Strategy1 #####################
names_population <- c("m40","m45","m50","m55","m60","m65","m70",
                        "f40","f45","f50","f55","f60","f65","f70")
result_m_M <- array(0, dim = c(10, 4, 14),
               dimnames = list(paste0("t",0:9), v_names_states, names_population))

for(i in 1:14){
  if(i != 7 && i != 14){
    a_P <- array(0, dim = c(n_states, n_states, 10),
               dimnames = list(v_names_states, v_names_states, 1:10))
    a_P["S1", "S1", 1:5] <- 1-(p_live_cvd[i]*(1-p_acvd_cvdth[i]) +
                               p_live_cvdth[i]*p_live_cvd[i]*p_acvd_cvdth[i] +
                               p_live_oth_death[i])
    a_P["S1", "S2", 1:5] <- p_live_cvd[i]*(1-p_acvd_cvdth[i])
    a_P["S1", "S3", 1:5] <- p_live_cvdth[i]*p_live_cvd[i]*p_acvd_cvdth[i]
    a_P["S1", "S4", 1:5] <- p_live_oth_death[i]
    a_P["S2", "S1", 1:5] <- 0
    a_P["S2", "S2", 1:5] <- 1-p_live_oth_death[i]-
      (p_ccvd_cvdth[i]+p_ccvd_acvd[i]*p_acvd_cvdth[i])
    a_P["S2", "S3", 1:5] <- p_ccvd_cvdth[i]+
      p_ccvd_acvd[i]*p_acvd_cvdth[i]
    a_P["S2", "S4", 1:5] <- p_live_oth_death[i]
    a_P["S3", "S3", 1:5] <- 1
    a_P["S4", "S4", 1:5] <- 1

    a_P["S1", "S1", 6:10] <-  1-(p_live_cvd[i+1]*(1-p_acvd_cvdth[i+1])+
                             p_live_cvdth[i+1]*p_live_cvd[i+1]*p_acvd_cvdth[i+1]
                             +p_live_oth_death[i+1])
    a_P["S1", "S2", 6:10] <- p_live_cvd[i+1]*(1-p_acvd_cvdth[i+1])
    a_P["S1", "S3", 6:10] <- p_live_cvdth[i+1]*p_live_cvd[i+1]*p_acvd_cvdth[i+1]
    a_P["S1", "S4", 6:10] <- p_live_oth_death[i+1]
    a_P["S2", "S1", 6:10] <- 0
    a_P["S2", "S2", 6:10] <- 1-p_live_oth_death[i+1]-
       (p_ccvd_cvdth[i+1]+p_ccvd_acvd[i+1]*p_acvd_cvdth[i+1])
    a_P["S2", "S3", 6:10] <- p_ccvd_cvdth[i+1]+p_ccvd_acvd[i+1]*p_acvd_cvdth[i+1]
    a_P["S2", "S4", 6:10] <-  p_live_oth_death[i+1]
    a_P["S3", "S3", 6:10] <- 1
    a_P["S4", "S4", 6:10] <- 1
  
    v_s_init <- c(state0 = 1, state1 = 0, state2 = 0, state3 = 0) 
    m_M <- matrix(0,nrow     = (n_t), ncol = n_states, 
                  dimnames = list(0:(n_t-1), v_names_states))
    m_M[1, ] <- v_s_init
    for(t in 1:9){
      m_M[t + 1, ] <- m_M[t, ] %*% a_P[, , t]
    }
    result_m_M[,,i] <- m_M
  }
    if(i == 7 | i == 14){
    a_P <- array(0, dim = c(n_states, n_states, 10),
               dimnames = list(v_names_states, v_names_states, 1:10))
    a_P["S1", "S1", 1:10] <- 1-(p_live_cvd[i]*(1-p_acvd_cvdth[i]) +
                               p_live_cvdth[i]*p_live_cvd[i]*p_acvd_cvdth[i] +
                               p_live_oth_death[i])
    a_P["S1", "S2", 1:10] <- p_live_cvd[i]*(1-p_acvd_cvdth[i])
    a_P["S1", "S3", 1:10] <- p_live_cvdth[i]*p_live_cvd[i]*p_acvd_cvdth[i]
    a_P["S1", "S4", 1:10] <- p_live_oth_death[i]
    a_P["S2", "S1", 1:10] <- 0
    a_P["S2", "S2", 1:10] <- 1-p_live_oth_death[i]-
      (p_ccvd_cvdth[i]+p_ccvd_acvd[i]*p_acvd_cvdth[i])
    a_P["S2", "S3", 1:10] <- p_ccvd_cvdth[i]+
      p_ccvd_acvd[i]*p_acvd_cvdth[i]
    a_P["S2", "S4", 1:10] <- p_live_oth_death[i]
    a_P["S3", "S3", 1:10] <- 1
    a_P["S4", "S4", 1:10] <- 1
    
    v_s_init <- c(state0 = 1, state1 = 0, state2 = 0, state3 = 0) 
    m_M <- matrix(0,nrow     = (n_t), ncol = n_states, 
                  dimnames = list(0:(n_t-1), v_names_states))
    m_M[1, ] <- v_s_init
    for(t in 1:9){
      m_M[t + 1, ] <- m_M[t, ] %*% a_P[, , t]
    }
    result_m_M[,,i] <- m_M
  }
}
result_m_M[ , ,1] # an example for the patient group 40-45, male
```

```{r results='asis'}
# p_acvd_cvdth
p8 <-array(runif(140,min=0.02,max=0.1),dim=c(10,14),dimnames=list(1:10,names_population))
p9 <- array(NA,dim=c(10,14),dimnames=list(1:10,names_population))
for (i in 1:14){
  if (i==7 | i==14){
    for (j in 1:10)
      p9[j,i]<-p_ccvd_acvd[i]*(1-p8[j,i])
  }
  else {
    for (j in 1:5){
      p9[j,i]<-p_ccvd_acvd[i]*(1-p8[j,i])
    }
    for (j in 6:10){
      p9[j,i]<-p_ccvd_acvd[i+1]*p8[j,i]
    }
  }
}
# print(xtable(data.frame(p9[,1:7]),digits=c(0,6,6,6,6,6,6,6),
#       caption = "Probability of CVD with CVD history (male)"),
#       caption.placement="top",comment=FALSE)
# print(xtable(data.frame(p9[,8:14]),digits=c(0,6,6,6,6,6,6,6),
#       caption = "Probability of CVD with CVD history (female)"),
#       caption.placement="top",comment=FALSE)
```


```{r results='asis'}
p10 <- array(NA,
             dim=c(10,14),
             dimnames=list(1:10,names_population))
for (i in 1:14){
  if (i==7 | i==14){
    for (j in 1:10)
      p10[j,i]<-p_live_cvd[i]
  }
  else {
    for (j in 1:5){
      p10[j,i]<-p_live_cvd[i]
    }
    for (j in 6:10){
      p10[j,i]<-p_live_cvd[i+1]
    }
  }
}
# print(xtable(data.frame(p10[,1:7]),digits=c(0,6,6,6,6,6,6,6),
#       caption = "Probability of first time CVD (male)"),
#       caption.placement="top",comment=FALSE)
# print(xtable(data.frame(p10[,8:14]),digits=c(0,6,6,6,6,6,6,6),
#       caption = "Probability of first time CVD (female)"),
#       caption.placement="top",comment=FALSE)

```


```{r results="asis"}
prob_group0 <- matrix(0, ncol=14, nrow=10,
                     dimnames=list(paste0("t",0:9),names_population))
patient_group <- matrix(noStrategy_data$num, ncol=1,
                        dimnames=list(names_population))
result_newCVD <- matrix(0,ncol = 1, nrow = 14,
                     dimnames=list(names_population,""))
result_liveCVD <- matrix(0,ncol = 1, nrow = 14,
                     dimnames=list(names_population,""))
reult_qaly <- matrix(0,ncol = 1, nrow = 14,
                     dimnames=list(names_population,""))
result_lifeyear <- matrix(0,ncol = 1, nrow = 14,
                     dimnames=list(names_population,""))
for (i in 1:14){
  # prob_group0[,i] <- result_m_M[, 1, i]* p_live_cvd[i]
  prob_group0[,i] <- result_m_M[, 1, i]* p10[,i]  # TODO
  # n_cnew[j+1,1,i]<-m_M[j,1,i] * p10[j,i]   ## new occurence = S1*p9
  result_newCVD[i] <- sum(prob_group0[,i]*patient_group[i]) # n_cnew
  
  # n_clive
  n_clive[j+1,1,i] <- sum(prob_group0[,i] * p)
  m_M[j,1,i]*a_P["s1","s2",j,i] +m_M[j,2,i]*p9[j,i]
    
  # qaly_m
  qaly_m[j+1,,i] <- m_M[j+1,,i] * uti + n_clive[j+1,1,i]*uti2
  # lifeyear_m
  lifeyear_m [j+1,,i] <- m_M[j+1,,i]*year
}

result_newCVD_stg0 <- sum(result_newCVD)
# print(xtable(data.frame(rbind(result_newCVD,"sum" = result_newCVD_stg0)),
#       caption = "CVD events for patients under Strategy0"),
#       caption.placement="top",comment=FALSE)

```

```{r}
HR_l_stg1	<- 0.63
HR_m_stg1	<- 1.56
HR_h_stg1	<- 1.6

HR_l_stg2	<- 0.43
HR_m_stg2	<- 0.97
HR_h_stg2	<- 2.06

HR_l_stg3	<- 0.45
HR_m_stg3	<- 1.09
HR_h_stg3	<- 2.11
# lifestyle intervention for medium risk and above
HR_smk_cvd	<-	0.85
HR_smk_cvdth	<-	0.72
HR_salt_cvd	<-	0.81
HR_salt_cvdth	<-	0.66
HR_wtc_cvd	<-	0.93
HR_wtc_dth	<-	0.93
# treatment intervention for high risk (additional)
HR_hpt_lip_cvd	<-	0.7
HR_hpt_lip_cvdth <-	0.82
```
\begin{center}
\begin{table}
\caption{Incidence rate}
\begin{tabular}{cccc} 
\hline
Item & & CVD incidence(HR) & CVD cause-specific mortality (HR)  \\
\hline
\multirow{3}{6em}{Strategy 1}& {Low risk} & `r HR_l_stg1` & 1   \\
& {Medium risk}& `r HR_m_stg1`  &  1\\
& {High risk}& `r HR_h_stg1`  &  1.7 \\
\hline
\multirow{3}{6em}{Strategy 2}& {Low risk}& `r HR_l_stg2`  & 1 \\
& {Medium risk}  & `r HR_m_stg2` &  1\\
& {High risk}  &`r HR_h_stg2`  &  1.7\\
\hline
\multirow{3}{6em}{Strategy 3}& {Low risk}  & `r HR_l_stg3` & 1 \\
& {Medium risk}  & `r HR_m_stg3` &  1\\
& {High risk}  & `r HR_h_stg3` &  1.7\\
\hline
\multirow{3}{6em}{Intervention}& {Weight control}  & `r HR_wtc_cvd` &  `r HR_wtc_dth`\\
& {Smoke cession}  & `r HR_smk_cvd` & `r HR_smk_cvdth` \\
& {Salt reduction}  & `r HR_salt_cvd` & `r HR_salt_cvdth` \\
\hline
Medication & Statin and antihypertensive & `r HR_hpt_lip_cvd` &  `r HR_hpt_lip_cvdth` \\
\hline
\end{tabular}
\end{table}
\end{center}

# Strategy 1

```{r}
p_live_cvd_l <- ProbFactor(p_live_cvd,HR_l_stg1)
p_live_cvd_m <- ProbFactor(p_live_cvd,HR_m_stg1*
                             HR_smk_cvd*HR_salt_cvd*HR_wtc_cvd)  # lifestyle intervention
p_live_cvd_h <- ProbFactor(p_live_cvd,HR_h_stg1*
                             HR_smk_cvdth*HR_salt_cvdth*HR_wtc_dth*    # lifestyle intervention
                             HR_hpt_lip_cvdth)   # treatment intervention 

# transition probability to death
p_live_cvdth_l <- ProbFactor(p_live_cvdth,1)    # equal
p_live_cvdth_m <- ProbFactor(p_live_cvdth,1*
                               HR_smk_cvd*HR_salt_cvd*HR_wtc_cvd)  # lifestyle intervention 
p_live_cvdth_h <- ProbFactor(p_live_cvdth,1.7*
                               HR_smk_cvdth*HR_salt_cvdth*HR_wtc_dth* # lifestyle intervention
                               HR_hpt_lip_cvdth) # treatment intervention 
```

```{r}
risk_levels <- c("low","medium","high")
result_newCVD_lmh <- matrix(0,  nrow = 14,ncol = 3,
                         dimnames = list(names_population, risk_levels))
p_live_cvd_lmh <- matrix(cbind(p_live_cvd_l,p_live_cvd_m,p_live_cvd_h), ncol=3,
                         dimnames = list(names_population,risk_levels))
p_live_cvdth_lmh <- matrix(cbind(p_live_cvdth_l,p_live_cvdth_m,p_live_cvdth_h), ncol=3,
                           dimnames = list(names_population,risk_levels))
for(r in 1:3){  # three rish groups
  for(i in 1:14){
  if(i != 7 && i != 14){
    a_P <- array(0, dim = c(n_states, n_states, 10),
               dimnames = list(v_names_states, v_names_states, 1:10))
    a_P["S1", "S1", 1:5] <- 1-(p_live_cvd_lmh[i,r]*(1-p_acvd_cvdth[i]) +
                               p_live_cvdth_lmh[i,r]*p_live_cvd_lmh[i,r]*p_acvd_cvdth[i] +
                               p_live_oth_death[i])
    a_P["S1", "S2", 1:5] <- p_live_cvd_lmh[i,r]*(1-p_acvd_cvdth[i])
    a_P["S1", "S3", 1:5] <- p_live_cvdth_lmh[i,r]*p_live_cvd_lmh[i,r]*p_acvd_cvdth[i]
    a_P["S1", "S4", 1:5] <- p_live_oth_death[i]
    a_P["S2", "S1", 1:5] <- 0
    a_P["S2", "S2", 1:5] <- 1-p_live_oth_death[i]-
      (p_ccvd_cvdth[i]+p_ccvd_acvd[i]*p_acvd_cvdth[i])
    a_P["S2", "S3", 1:5] <- p_ccvd_cvdth[i]+
      p_ccvd_acvd[i]*p_acvd_cvdth[i]
    a_P["S2", "S4", 1:5] <- p_live_oth_death[i]
    a_P["S3", "S3", 1:5] <- 1
    a_P["S4", "S4", 1:5] <- 1

    a_P["S1", "S1", 6:10] <-  1-(p_live_cvd_lmh[i+1]*(1-p_acvd_cvdth[i+1])+
                             p_live_cvdth_lmh[i+1]*p_live_cvd_lmh[i+1]*p_acvd_cvdth[i+1]
                             +p_live_oth_death[i+1])
    a_P["S1", "S2", 6:10] <- p_live_cvd_lmh[i+1]*(1-p_acvd_cvdth[i+1])
    a_P["S1", "S3", 6:10] <- p_live_cvdth_lmh[i+1]*p_live_cvd_lmh[i+1]*p_acvd_cvdth[i+1]
    a_P["S1", "S4", 6:10] <- p_live_oth_death[i+1]
    a_P["S2", "S1", 6:10] <- 0
    a_P["S2", "S2", 6:10] <- 1-p_live_oth_death[i+1]-
       (p_ccvd_cvdth[i+1]+p_ccvd_acvd[i+1]*p_acvd_cvdth[i+1])
    a_P["S2", "S3", 6:10] <- p_ccvd_cvdth[i+1]+p_ccvd_acvd[i+1]*p_acvd_cvdth[i+1]
    a_P["S2", "S4", 6:10] <-  p_live_oth_death[i+1]
    a_P["S3", "S3", 6:10] <- 1
    a_P["S4", "S4", 6:10] <- 1
  
    v_s_init <- c(state0 = 1, state1 = 0, state2 = 0, state3 = 0) 
    m_M <- matrix(0,nrow     = (n_t), ncol = n_states, 
                  dimnames = list(0:(n_t-1), v_names_states))
    m_M[1, ] <- v_s_init
    for(t in 1:9){
      m_M[t + 1, ] <- m_M[t, ] %*% a_P[, , t]
    }
    result_m_M[,,i] <- m_M
  }
    if(i == 7 | i == 14){
    a_P <- array(0, dim = c(n_states, n_states, 10),
               dimnames = list(v_names_states, v_names_states, 1:10))
    a_P["S1", "S1", 1:10] <- 1-(p_live_cvd[i]*(1-p_acvd_cvdth[i]) +
                               p_live_cvdth[i]*p_live_cvd[i]*p_acvd_cvdth[i] +
                               p_live_oth_death[i])
    a_P["S1", "S2", 1:10] <- p_live_cvd[i]*(1-p_acvd_cvdth[i])
    a_P["S1", "S3", 1:10] <- p_live_cvdth[i]*p_live_cvd[i]*p_acvd_cvdth[i]
    a_P["S1", "S4", 1:10] <- p_live_oth_death[i]
    a_P["S2", "S1", 1:10] <- 0
    a_P["S2", "S2", 1:10] <- 1-p_live_oth_death[i]-
      (p_ccvd_cvdth[i]+p_ccvd_acvd[i]*p_acvd_cvdth[i])
    a_P["S2", "S3", 1:10] <- p_ccvd_cvdth[i]+
      p_ccvd_acvd[i]*p_acvd_cvdth[i]
    a_P["S2", "S4", 1:10] <- p_live_oth_death[i]
    a_P["S3", "S3", 1:10] <- 1
    a_P["S4", "S4", 1:10] <- 1
    
    v_s_init <- c(state0 = 1, state1 = 0, state2 = 0, state3 = 0) 
    m_M <- matrix(0,nrow     = (n_t), ncol = n_states, 
                  dimnames = list(0:(n_t-1), v_names_states))
    m_M[1, ] <- v_s_init
    for(t in 1:9){
      m_M[t + 1, ] <- m_M[t, ] %*% a_P[, , t]
    }
    result_m_M[,,i] <- m_M
  }
}
  
prob_group1 <- matrix(0, ncol=14, nrow=10,
                     dimnames=list(paste0("t",0:9),names_population))
for (i in 1:14){
  prob_group1[,i] <- result_m_M[, 1, i]* p_live_cvd_lmh[i,r]
}
patient_group <- matrix(cbind(population_data[1:14,]$low,
                              population_data[1:14,]$medium,
                              population_data[1:14,]$high),
       ncol = 3, nrow=14,dimnames = list(names_population,risk_levels))
for(j in 1:14){
  result_newCVD_lmh[j,r] <- sum(prob_group1[,j]*patient_group[j,r]) 
} 
}
```


```{r results="asis"}
print(xtable((rbind(result_newCVD_lmh, "sum" = colSums(result_newCVD_lmh))),
      caption = "CVD events for patients under Strategy1"),
      caption.placement="top",comment=FALSE)
result_newCVD_stg1 <- sum(result_newCVD_lmh)
result_newCVD_stg1
```




# Strategy 2
```{r}
p_live_cvd_l <- ProbFactor(p_live_cvd,HR_l_stg2)
p_live_cvd_m <- ProbFactor(p_live_cvd,HR_m_stg2*
                             HR_smk_cvd*HR_salt_cvd*HR_wtc_cvd)  # lifestyle intervention
p_live_cvd_h <- ProbFactor(p_live_cvd,HR_h_stg2*
                             HR_smk_cvdth*HR_salt_cvdth*HR_wtc_dth*    # lifestyle intervention
                             HR_hpt_lip_cvdth)   # treatment intervention 

# transition probability to death
p_live_cvdth_l <- ProbFactor(p_live_cvdth,1)    # equal
p_live_cvdth_m <- ProbFactor(p_live_cvdth,1*
                               HR_smk_cvd*HR_salt_cvd*HR_wtc_cvd)  # lifestyle intervention 
p_live_cvdth_h <- ProbFactor(p_live_cvdth,1.7*
                               HR_smk_cvdth*HR_salt_cvdth*HR_wtc_dth* # lifestyle intervention
                               HR_hpt_lip_cvdth) # treatment intervention 
```

```{r}
risk_levels <- c("low","medium","high")
result_newCVD_lmh <- matrix(0,  nrow = 14,ncol = 3,
                         dimnames = list(names_population, risk_levels))
p_live_cvd_lmh <- matrix(cbind(p_live_cvd_l,p_live_cvd_m,p_live_cvd_h), ncol=3,
                         dimnames = list(names_population,risk_levels))
p_live_cvdth_lmh <- matrix(cbind(p_live_cvdth_l,p_live_cvdth_m,p_live_cvdth_h), ncol=3,
                           dimnames = list(names_population,risk_levels))
for(r in 1:3){  # three rish groups
  for(i in 1:14){
  if(i != 7 && i != 14){
    a_P <- array(0, dim = c(n_states, n_states, 10),
               dimnames = list(v_names_states, v_names_states, 1:10))
    a_P["S1", "S1", 1:5] <- 1-(p_live_cvd_lmh[i,r]*(1-p_acvd_cvdth[i]) +
                               p_live_cvdth_lmh[i,r]*p_live_cvd_lmh[i,r]*p_acvd_cvdth[i] +
                               p_live_oth_death[i])
    a_P["S1", "S2", 1:5] <- p_live_cvd_lmh[i,r]*(1-p_acvd_cvdth[i])
    a_P["S1", "S3", 1:5] <- p_live_cvdth_lmh[i,r]*p_live_cvd_lmh[i,r]*p_acvd_cvdth[i]
    a_P["S1", "S4", 1:5] <- p_live_oth_death[i]
    a_P["S2", "S1", 1:5] <- 0
    a_P["S2", "S2", 1:5] <- 1-p_live_oth_death[i]-
      (p_ccvd_cvdth[i]+p_ccvd_acvd[i]*p_acvd_cvdth[i])
    a_P["S2", "S3", 1:5] <- p_ccvd_cvdth[i]+
      p_ccvd_acvd[i]*p_acvd_cvdth[i]
    a_P["S2", "S4", 1:5] <- p_live_oth_death[i]
    a_P["S3", "S3", 1:5] <- 1
    a_P["S4", "S4", 1:5] <- 1

    a_P["S1", "S1", 6:10] <-  1-(p_live_cvd_lmh[i+1]*(1-p_acvd_cvdth[i+1])+
                             p_live_cvdth_lmh[i+1]*p_live_cvd_lmh[i+1]*p_acvd_cvdth[i+1]
                             +p_live_oth_death[i+1])
    a_P["S1", "S2", 6:10] <- p_live_cvd_lmh[i+1]*(1-p_acvd_cvdth[i+1])
    a_P["S1", "S3", 6:10] <- p_live_cvdth_lmh[i+1]*p_live_cvd_lmh[i+1]*p_acvd_cvdth[i+1]
    a_P["S1", "S4", 6:10] <- p_live_oth_death[i+1]
    a_P["S2", "S1", 6:10] <- 0
    a_P["S2", "S2", 6:10] <- 1-p_live_oth_death[i+1]-
       (p_ccvd_cvdth[i+1]+p_ccvd_acvd[i+1]*p_acvd_cvdth[i+1])
    a_P["S2", "S3", 6:10] <- p_ccvd_cvdth[i+1]+p_ccvd_acvd[i+1]*p_acvd_cvdth[i+1]
    a_P["S2", "S4", 6:10] <-  p_live_oth_death[i+1]
    a_P["S3", "S3", 6:10] <- 1
    a_P["S4", "S4", 6:10] <- 1
  
    v_s_init <- c(state0 = 1, state1 = 0, state2 = 0, state3 = 0) 
    m_M <- matrix(0,nrow     = (n_t), ncol = n_states, 
                  dimnames = list(0:(n_t-1), v_names_states))
    m_M[1, ] <- v_s_init
    for(t in 1:9){
      m_M[t + 1, ] <- m_M[t, ] %*% a_P[, , t]
    }
    result_m_M[,,i] <- m_M
  }
    if(i == 7 | i == 14){
    a_P <- array(0, dim = c(n_states, n_states, 10),
               dimnames = list(v_names_states, v_names_states, 1:10))
    a_P["S1", "S1", 1:10] <- 1-(p_live_cvd[i]*(1-p_acvd_cvdth[i]) +
                               p_live_cvdth[i]*p_live_cvd[i]*p_acvd_cvdth[i] +
                               p_live_oth_death[i])
    a_P["S1", "S2", 1:10] <- p_live_cvd[i]*(1-p_acvd_cvdth[i])
    a_P["S1", "S3", 1:10] <- p_live_cvdth[i]*p_live_cvd[i]*p_acvd_cvdth[i]
    a_P["S1", "S4", 1:10] <- p_live_oth_death[i]
    a_P["S2", "S1", 1:10] <- 0
    a_P["S2", "S2", 1:10] <- 1-p_live_oth_death[i]-
      (p_ccvd_cvdth[i]+p_ccvd_acvd[i]*p_acvd_cvdth[i])
    a_P["S2", "S3", 1:10] <- p_ccvd_cvdth[i]+
      p_ccvd_acvd[i]*p_acvd_cvdth[i]
    a_P["S2", "S4", 1:10] <- p_live_oth_death[i]
    a_P["S3", "S3", 1:10] <- 1
    a_P["S4", "S4", 1:10] <- 1
    
    v_s_init <- c(state0 = 1, state1 = 0, state2 = 0, state3 = 0) 
    m_M <- matrix(0,nrow     = (n_t), ncol = n_states, 
                  dimnames = list(0:(n_t-1), v_names_states))
    m_M[1, ] <- v_s_init
    for(t in 1:9){
      m_M[t + 1, ] <- m_M[t, ] %*% a_P[, , t]
    }
    result_m_M[,,i] <- m_M
  }
}

prob_group2 <- matrix(0, ncol=14, nrow=10,
                     dimnames=list(paste0("t",0:9),names_population))
for (i in 1:14){
  prob_group2[,i] <- result_m_M[, 1, i]* p_live_cvd_lmh[i,r]
}
patient_group <- matrix(cbind(population_data[15:28,]$low,
                              population_data[15:28,]$medium,
                              population_data[15:28,]$high),
       ncol = 3, nrow=14,dimnames = list(names_population,risk_levels))
result_newCVD <- matrix(NA)
for(j in 1:14){
  result_newCVD_lmh[j,r] <- sum(prob_group2[,j]*patient_group[j,r])
} 
}
```


```{r results="asis"}
print(xtable((rbind(result_newCVD_lmh, "sum" = colSums(result_newCVD_lmh))),
      caption = "CVD events for patients under Strategy2"),
      caption.placement="top",comment=FALSE)
result_newCVD_stg2 <- sum(result_newCVD_lmh)
result_newCVD_stg2
```

# Strategy 3

```{r}
p_live_cvd_l <- ProbFactor(p_live_cvd,HR_l_stg3)
p_live_cvd_m <- ProbFactor(p_live_cvd,HR_m_stg3*
                             HR_smk_cvd*HR_salt_cvd*HR_wtc_cvd)  # lifestyle intervention
p_live_cvd_h <- ProbFactor(p_live_cvd,HR_h_stg3*
                             HR_smk_cvdth*HR_salt_cvdth*HR_wtc_dth*    # lifestyle intervention
                             HR_hpt_lip_cvdth)   # treatment intervention 

# transition probability to death
p_live_cvdth_l <- ProbFactor(p_live_cvdth,1)    # equal
p_live_cvdth_m <- ProbFactor(p_live_cvdth,1*
                               HR_smk_cvd*HR_salt_cvd*HR_wtc_cvd)  # lifestyle intervention 
p_live_cvdth_h <- ProbFactor(p_live_cvdth,1.7*
                               HR_smk_cvdth*HR_salt_cvdth*HR_wtc_dth* # lifestyle intervention
                               HR_hpt_lip_cvdth) # treatment intervention 
```


```{r}
risk_levels <- c("low","medium","high")
result_newCVD_lmh <- matrix(0,  nrow = 14,ncol = 3,
                         dimnames = list(names_population, risk_levels))
p_live_cvd_lmh <- matrix(cbind(p_live_cvd_l,p_live_cvd_m,p_live_cvd_h), ncol=3,
                         dimnames = list(names_population,risk_levels))
p_live_cvdth_lmh <- matrix(cbind(p_live_cvdth_l,p_live_cvdth_m,p_live_cvdth_h), ncol=3,
                           dimnames = list(names_population,risk_levels))
for(r in 1:3){  # three rish groups
  for(i in 1:14){
  if(i != 7 && i != 14){
    a_P <- array(0, dim = c(n_states, n_states, 10),
               dimnames = list(v_names_states, v_names_states, 1:10))
    a_P["S1", "S1", 1:5] <- 1-(p_live_cvd_lmh[i,r]*(1-p_acvd_cvdth[i]) +
                               p_live_cvdth_lmh[i,r]*p_live_cvd_lmh[i,r]*p_acvd_cvdth[i] +
                               p_live_oth_death[i])
    a_P["S1", "S2", 1:5] <- p_live_cvd_lmh[i,r]*(1-p_acvd_cvdth[i])
    a_P["S1", "S3", 1:5] <- p_live_cvdth_lmh[i,r]*p_live_cvd_lmh[i,r]*p_acvd_cvdth[i]
    a_P["S1", "S4", 1:5] <- p_live_oth_death[i]
    a_P["S2", "S1", 1:5] <- 0
    a_P["S2", "S2", 1:5] <- 1-p_live_oth_death[i]-
      (p_ccvd_cvdth[i]+p_ccvd_acvd[i]*p_acvd_cvdth[i])
    a_P["S2", "S3", 1:5] <- p_ccvd_cvdth[i]+
      p_ccvd_acvd[i]*p_acvd_cvdth[i]
    a_P["S2", "S4", 1:5] <- p_live_oth_death[i]
    a_P["S3", "S3", 1:5] <- 1
    a_P["S4", "S4", 1:5] <- 1

    a_P["S1", "S1", 6:10] <-  1-(p_live_cvd_lmh[i+1]*(1-p_acvd_cvdth[i+1])+
                             p_live_cvdth_lmh[i+1]*p_live_cvd_lmh[i+1]*p_acvd_cvdth[i+1]
                             +p_live_oth_death[i+1])
    a_P["S1", "S2", 6:10] <- p_live_cvd_lmh[i+1]*(1-p_acvd_cvdth[i+1])
    a_P["S1", "S3", 6:10] <- p_live_cvdth_lmh[i+1]*p_live_cvd_lmh[i+1]*p_acvd_cvdth[i+1]
    a_P["S1", "S4", 6:10] <- p_live_oth_death[i+1]
    a_P["S2", "S1", 6:10] <- 0
    a_P["S2", "S2", 6:10] <- 1-p_live_oth_death[i+1]-
       (p_ccvd_cvdth[i+1]+p_ccvd_acvd[i+1]*p_acvd_cvdth[i+1])
    a_P["S2", "S3", 6:10] <- p_ccvd_cvdth[i+1]+p_ccvd_acvd[i+1]*p_acvd_cvdth[i+1]
    a_P["S2", "S4", 6:10] <-  p_live_oth_death[i+1]
    a_P["S3", "S3", 6:10] <- 1
    a_P["S4", "S4", 6:10] <- 1
  
    v_s_init <- c(state0 = 1, state1 = 0, state2 = 0, state3 = 0) 
    m_M <- matrix(0,nrow     = (n_t), ncol = n_states, 
                  dimnames = list(0:(n_t-1), v_names_states))
    m_M[1, ] <- v_s_init
    for(t in 1:9){
      m_M[t + 1, ] <- m_M[t, ] %*% a_P[, , t]
    }
    result_m_M[,,i] <- m_M
  }
    if(i == 7 | i == 14){
    a_P <- array(0, dim = c(n_states, n_states, 10),
               dimnames = list(v_names_states, v_names_states, 1:10))
    a_P["S1", "S1", 1:10] <- 1-(p_live_cvd[i]*(1-p_acvd_cvdth[i]) +
                               p_live_cvdth[i]*p_live_cvd[i]*p_acvd_cvdth[i] +
                               p_live_oth_death[i])
    a_P["S1", "S2", 1:10] <- p_live_cvd[i]*(1-p_acvd_cvdth[i])
    a_P["S1", "S3", 1:10] <- p_live_cvdth[i]*p_live_cvd[i]*p_acvd_cvdth[i]
    a_P["S1", "S4", 1:10] <- p_live_oth_death[i]
    a_P["S2", "S1", 1:10] <- 0
    a_P["S2", "S2", 1:10] <- 1-p_live_oth_death[i]-
      (p_ccvd_cvdth[i]+p_ccvd_acvd[i]*p_acvd_cvdth[i])
    a_P["S2", "S3", 1:10] <- p_ccvd_cvdth[i]+
      p_ccvd_acvd[i]*p_acvd_cvdth[i]
    a_P["S2", "S4", 1:10] <- p_live_oth_death[i]
    a_P["S3", "S3", 1:10] <- 1
    a_P["S4", "S4", 1:10] <- 1
    
    v_s_init <- c(state0 = 1, state1 = 0, state2 = 0, state3 = 0) 
    m_M <- matrix(0,nrow     = (n_t), ncol = n_states, 
                  dimnames = list(0:(n_t-1), v_names_states))
    m_M[1, ] <- v_s_init
    for(t in 1:9){
      m_M[t + 1, ] <- m_M[t, ] %*% a_P[, , t]
    }
    result_m_M[,,i] <- m_M
  }
}

prob_group3 <- matrix(0, ncol=14, nrow=10,
                     dimnames=list(paste0("t",0:9),names_population))
for (i in 1:14){
  prob_group3[,i] <- result_m_M[, 1, i]* p_live_cvd_lmh[i,r]
}

patient_group <- matrix(cbind(population_data[29:42,]$low,
                              population_data[29:42,]$medium,
                              population_data[29:42,]$high),
       ncol = 3, nrow=14,dimnames = list(names_population,risk_levels))
result_newCVD <- matrix(NA)
for(j in 1:14){
  result_newCVD_lmh[j,r] <- sum(prob_group3[,j]*patient_group[j,r])
} 
}
```

```{r, results="asis"}
print(xtable((rbind(result_newCVD_lmh, "sum" = colSums(result_newCVD_lmh))),
      caption = "CVD events for patients under Strategy3"),
      caption.placement="top",comment=FALSE)
result_newCVD_stg3 <- sum(result_newCVD_lmh)
result_newCVD_stg3
```

# Conclusion

```{r results="asis"}
print(xtable((matrix(cbind(result_newCVD_stg0,result_newCVD_stg1,
      result_newCVD_stg2,result_newCVD_stg3),nrow = 1, ncol = 4,
      dimnames = list("",v_names_str))),
      caption = "CVD events for patients under 3 strategies"),
      caption.placement="top",comment=FALSE)

```

